Visualization of [fulle name] Fractional Integrals

### 2019-04-14 fractional/CMJ style files/article-template.tex
added another paragraph to the article

To make things clearer lets set the value of $\alpha$ to $0.8$ and the value of $t$ to 10 and then depict the region associated that is associated with the Cavalieri integral which is obtained

>>>>

Lets clarify the above by working through a detailed example. Lets set the value of $\alpha$ to $\frac{4}{5}$ and the value of $t$ to 10 and then convert the 
integrals in ?? and ?? to equivalent Cavalieri integrals. If we evaluate these Cavalieri integrals we obtain the area of two regions $A$ and $B$. Both $A$ and $B$ are bounded by the $x$-axis, 
$f(x)$ and $b_{10}^{\frac{4}{5}}(y)$. Region $A$ and $B$ are depicted in the rightmost panel of Fig ?? and Fig ??. Note that the curves $\{b_{t}^{\frac{4}{5}}(y)|t\in\{2,4,6,8,10\}\}$ are plotted 
using a greyscale. The shade with which $b_t^{\alpha}(y)$ is depicted becomes lighter as the value of $t$ increases.  is the lighter the curve associated with $b_t^{\alpha}(y)$ is.

We depict We depict $b_10^{\alpha}(y)$ with the lightest
shade of
depicted in the right most   depict the region associated that is associated with the Cavalieri integral which is obtained
